Viscous Transport in Eroding Porous Media

### 2019-05-02 docs/transport/erosion_transport.tex
doing in tranposrt paper

\displaystyle\frac{\partial u_1(\xx)}{x_1} & \displaystyle\frac{\partial u_1(\xx)}{x_2}\\ \\
\displaystyle\frac{\partial u_2(\xx)}{x_1} & \displaystyle\frac{\partial u_2(\xx)}{x_2}

@@

\frac{\partial u_1(\xx)}{x_1}&= \Re (v'[\tau_1](x)) + \Re (v''[\yy\cdot\eeta](x)) 

@@

\frac{\partial u_1(\xx)}{x_2}&= - \operatorname{Im} (v'[\tau_1](x)) 

@@

\frac{\partial u_2(\xx)}{x_1}&= \Re (v'[\tau_2](x)) 

@@

\frac{\partial u_2(\xx)}{x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 

@@

{\color{red}
 Let $L_w$ be the length of the outer boundary and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$. Here are the criteria to see if two points are too close for trapezoid. For criterion of outer boundary to body,  let $d$ be the minimum distance between outer boundary and a point $x$ on the body $b$, we say $x$ is too close to wall if
$$d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}$$
where $\alpha_1$ is a constant. 
For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
$$d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_2}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)$$
where $\alpha_2$ is a constant.

>>>>

\displaystyle\frac{\partial u_1(\xx)}{\partial x_1} & 
\displaystyle\frac{\partial u_1(\xx)}{\partial x_2}\\ \\
\displaystyle\frac{\partial u_2(\xx)}{\partial x_1} & 
\displaystyle\frac{\partial u_2(\xx)}{\partial x_2}

@@

\frac{\partial u_1(\xx)}{\partial x_1}&= \Re (v'[\tau_1](x)) + \Re (v''[\yy\cdot\eeta](x)) 

@@

\frac{\partial u_1(\xx)}{\partial x_2}&= - \operatorname{Im} (v'[\tau_1](x)) 

@@

\frac{\partial u_2(\xx)}{\partial x_1}&= \Re (v'[\tau_2](x)) 

@@

\frac{\partial u_2(\xx)}{\partial x_2}&= -\operatorname{Im} (v'[\tau_2](x)) 

@@

{\color{red}
 Let $L_w$ be the length of the outer boundary and $L_{b}$ be the length of the boundary of body where $b=1, \cdots, M$. Here are the criteria to see if two points are too close for trapezoid. For criterion of outer boundary to body,  let $d$ be the minimum distance between outer boundary and a point $x$ on the body $b$, we say $x$ is too close to outer boundary if
$$d<\frac{L_{b}}{2\pi} + \alpha_1\frac{L_w}{N_\out}$$
where $\alpha_1$ is a constant. 
For criterion between two bodies, let $d$ be the distance between the centroid $a$ of the body $b_1$ and a point $x$ on the body $b_2$, we say they are too close if
$$d<\frac{L_{b_1}}{2\pi}+\frac{L_{b_2}}{2\pi}+\alpha_2\left(\frac{L_{b_1}}{N_\iin}+\frac{L_{b_2}}{N_\iin}\right)$$
where $\alpha_2$ is a constant.
